Think deep for reef resilience

### 2025-06-26 paper/paper_draft.qmd
Add writing of median timeseries to script for easier data sharing

![Reef Degree Heating Week timeseries clustered within each management area, for each GCM analysed. ‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each bioregion. ‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each bioregion. ‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each bioregion. Solid lines represent the cluster median timeseries and bands represent the 2.5 to 97.5 percentile confidence intervals. Each management area is represented five times (for each GCM), with each GCM displayed horizontally.](/../outputs/ADRIA_results/HighResCoralStress/figs/GCM_timeseries_plot.png){#fig-gcm-trajectories width=`{julia} timeseries_width`}

@@

![Mean timeseries DHW values for reefs within each bioregion, separated into clusters assigned by timeseries clustering. ‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each bioregion. ‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each bioregion. ‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each bioregion. Solid lines represent the median DHW level for each cluster. Displays results for ACCESS-ESM1-5 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/mean_dhw_bioregion_violin.png){#fig-access-esm1-5-bioregion-dhwmean width=`{julia} violin_width`}

@@

![Reef relative coral cover timeseries clustered within each management area. ‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each management area. ‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each management area. ‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each management area. Solid lines represent the cluster median timeseries and bands represent the 2.5 to 97.5 percentile confidence intervals. Displays results for ACCESS-ESM1-5 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/management_area/management_area_cover_timeseries.png){#fig-access-esm1-5-manarea-timeseries width=`{julia} timeseries_width`}

![Median depth for reefs within each management area, separated into clusters assigned by timeseries clustering. ‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each management area. ‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each management area. ‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each management area. Solid lines represent the median depth for each cluster and grey points represent the depth value for each reef. Displays results for ACCESS-ESM1-5 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/management_area/depth_management_area_violin.png){#fig-access-esm1-5-manarea-depth width=`{julia} violin_width`}

@@

![Reef relative coral cover timeseries clustered across the Great Barrier Reef. The ‘Low’ cluster (green) is the cluster with the lowest median relative cover between 2030 and 2040. The ‘Medium’ cluster (orange) is the cluster with intermediate median relative cover between 2030 and 2040. The ‘High’ cluster (blue) is the cluster with the highest median relative cover between 2030 and 2040. Solid lines represent the cluster median timeseries and bands represent the 2.5 to 97.5 percentile confidence intervals. Displays results for ACCESS-ESM1-5 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/gbr/gbr_cover_timeseries.png){#fig-access-esm1-5-gbr-timeseries width=`{julia} timeseries_width`}

![Median depth for reefs, separated into clusters assigned by timeseries clustering. ‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040. ‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040. ‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040. Solid lines represent the median depth for each cluster and grey points represent the depth value for each reef. Displays results for ACCESS-ESM1-5 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/gbr/depth_gbr_violin.png){#fig-access-esm1-5-gbr-depth width=`{julia} violin_width`}

>>>>

![Reef Degree Heating Week timeseries clustered within each management area, for each GCM analysed. ‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each bioregion. ‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each bioregion. ‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each bioregion. Solid lines represent the cluster median timeseries and bands represent the 2.5 to 97.5 percentile confidence intervals. Each management area is represented five times (for each GCM), with each GCM displayed horizontally.](/../outputs/ADRIA_results/HighResCoralStress/figs/GCM_timeseries_plot.png){#sfig-gcm-trajectories width=`{julia} timeseries_width`}

@@

![Mean timeseries DHW values for reefs within each bioregion, separated into clusters assigned by timeseries clustering. ‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each bioregion. ‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each bioregion. ‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each bioregion. Solid lines represent the median DHW level for each cluster. Displays results for ACCESS-ESM1-5 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/mean_dhw_bioregion_violin.png){#sfig-access-esm1-5-bioregion-dhwmean width=`{julia} violin_width`}

@@

![Reef relative coral cover timeseries clustered within each management area. ‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each management area. ‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each management area. ‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each management area. Solid lines represent the cluster median timeseries and bands represent the 2.5 to 97.5 percentile confidence intervals. Displays results for ACCESS-ESM1-5 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/management_area/management_area_cover_timeseries.png){#sfig-access-esm1-5-manarea-timeseries width=`{julia} timeseries_width`}

![Median depth for reefs within each management area, separated into clusters assigned by timeseries clustering. ‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each management area. ‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each management area. ‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each management area. Solid lines represent the median depth for each cluster and grey points represent the depth value for each reef. Displays results for ACCESS-ESM1-5 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/management_area/depth_management_area_violin.png){#sfig-access-esm1-5-manarea-depth width=`{julia} violin_width`}

@@

![Reef relative coral cover timeseries clustered across the Great Barrier Reef. The ‘Low’ cluster (green) is the cluster with the lowest median relative cover between 2030 and 2040. The ‘Medium’ cluster (orange) is the cluster with intermediate median relative cover between 2030 and 2040. The ‘High’ cluster (blue) is the cluster with the highest median relative cover between 2030 and 2040. Solid lines represent the cluster median timeseries and bands represent the 2.5 to 97.5 percentile confidence intervals. Displays results for ACCESS-ESM1-5 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/gbr/gbr_cover_timeseries.png){#sfig-access-esm1-5-gbr-timeseries width=`{julia} timeseries_width`}

![Median depth for reefs, separated into clusters assigned by timeseries clustering. ‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040. ‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040. ‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040. Solid lines represent the median depth for each cluster and grey points represent the depth value for each reef. Displays results for ACCESS-ESM1-5 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/gbr/depth_gbr_violin.png){#sfig-access-esm1-5-gbr-depth width=`{julia} violin_width`}
